SunPy - Python for Solar Physics

### 2014-08-25 2-1-Map.tex

\begin{listing}[H]
\pythoncode{map1.py}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

In addition to the data-type classes, the \texttt{map} subpackage provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
temporally and spatially aligned data respectively.
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.
\texttt{MapCube} provides methods for animation of its series of \texttt{Map} 
objects. Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to 
interact with these classes.

\begin{listing}[H]
\pythoncode{map2.py}
\begin{center}
\includegraphics[width=0.8\columnwidth]{comp_map_example}
\end{center}
\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
\label{code:compmap_1}
\end{listing}

\begin{listing}[H]
\pythoncode{map3.py}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
\end{center}
\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 
through the \texttt{MapCube}.}
\label{code:mapcube_1}
\end{listing}

>>>>

\begin{listing}[H]
\pythoncode{pycode_map1.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_map_example}
\end{center}
\caption{Example of the \texttt{AIAMap} specialisation of 
\texttt{GenericMap}. The map is created from an \textit{SDO}/AIA FITS file, a cutout
of the map is created, and then a quick-view plot is created with lines of heliographic longitude and latitude over-plotted.}
\label{code:aia_1}
\end{listing}

In addition to the data-type classes, the \texttt{map} subpackage provides two 
collection classes, \texttt{CompositeMap} and \texttt{MapCube}, for 
spatially and temporally aligned data respectively.
\texttt{CompositeMap} provides methods for overlaying spatially aligned 
data, with support for visualisation of images and contour lines overlaid 
upon each other.
\texttt{MapCube} provides methods for animation of its series of \texttt{Map} 
objects. Listings~\ref{code:compmap_1} and \ref{code:mapcube_1} show how to 
interact with these classes.

\begin{listing}[H]
\pythoncode{pycode_map2.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{comp_map_example}
\end{center}
\caption{Example showing the functionality of \texttt{CompositeMap}, with RHESSI data composited
on top of \textit{SDO}/AIA data. The \texttt{CompositeMap} is plotted using the integration with the \texttt{matplotlib.pyplot} interface.}
\label{code:compmap_1}
\end{listing}

\begin{listing}[H]
\pythoncode{pycode_map3.txt}
\begin{center}
\includegraphics[width=0.8\columnwidth]{aia_cube_controls}
\end{center}
\caption{Example showing the creation of a \texttt{MapCube} from a list of files. The 
resultant plot makes use of \texttt{matplotlib}'s interactive widgets to allow scrolling 
through the \texttt{MapCube}.}
\label{code:mapcube_1}
\end{listing}

### 2014-08-25 3-2-HEK.tex

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> from sunpy.net import hek
>>> client = hek.HEKClient()
>>> tstart, tend = "2011/08/09 00:00:00", "2011/08/10 00:00:00"
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType("FL")) # flares
>>> len(result)
52
\end{minted}
\caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
on 2011 August 9.}
\label{code:hek:simple}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType("FL"),
...                       hek.attrs.FRM.Name=="SSW Latest Events")
>>> len(result)
9
\end{minted}
\caption{An HEK query that returns only those flares that were
  detected by the `SSW Latest Events' feature recognition method.}
\label{code:hek:frm}
\end{listing}

@@

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> result = client.query(hek.attrs.Time(tstart, tend), 
...                       hek.attrs.EventType("FL"),
...                       (hek.attrs.Event.Coord1>50) 
...                       or (hek.attrs.FL.PeakFlux>1000.0))
\end{minted}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes, but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.

Frequently after users have found events of interest the next step is to 
download observational data. The \texttt{H2VClient} module makes this
much easier by providing a translation layer between HEK query results
and VSO queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.
\begin{listing}[H]
\begin{minted}[bgcolor=bg]{python}
>>> from sunpy.net import hek2vso
>>> h2v = hek2vso.H2VClient()
>>> vso_results = h2v.translate_and_query(result[0])
>>> h2v.vso_client.get(vso_results[0]).wait()
\end{minted}
\caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 
query and download of data from the first HEK result from the VSO.}
\label{code:hek2vso}
\end{listing}

>>>>

\begin{listing}[H]
\pythoncode{pycode_hek.txt}
\caption{Example usage of the \texttt{hek} module showing a simple HEK search for solar flares
on 2011 August 9.}
\label{code:hek:simple}
\end{listing}

@@

\begin{listing}[H]
\pythoncode{pycode_hek2.txt}
\caption{An HEK query that returns only those flares that were
  detected by the `SSW Latest Events' feature recognition method.}
\label{code:hek:frm}
\end{listing}

@@

\begin{listing}[H]
\pythoncode{pycode_hek3.txt}
\caption{HEK query using the logical \texttt{or} operator.}
\label{code:hek:or}
\end{listing}
All FRMs report the required feature attributes, but the optional attributes 
are FRM dependent.  If a FRM does not have one of the optional attributes, 
\texttt{None} is returned by the \texttt{hek} module.

Frequently after users have found events of interest the next step is to 
download observational data. The \texttt{H2VClient} module makes this
much easier by providing a translation layer between HEK query results
and VSO queries. This capability is demonstrated in Listing~\ref{code:hek2vso}.
\begin{listing}[H]
\pythoncode{pycode_hek4.txt}
\caption{Code snippet continuing from Listing~\ref{code:hek:or} showing the 
query and download of data from the first HEK result from the VSO.}
\label{code:hek2vso}
\end{listing}

### 2014-08-25 4-Util.tex

\begin{listing}[H]
\pythoncode{util1.py}
\caption{Using the \texttt{wcs} subpackage.}
\label{code:wcs_code}
\end{listing}

@@

The \texttt{sun.constants} module provides a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values  within the SunPy code base, but also to the user. Every solar 
constant is provided as a \texttt{Constant} object as defined by Astropy. Each 
\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
the constant's provenance (i.e., reference) and its uncertainty. Using 
Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modelled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

\begin{listing}[H]
\pythoncode{util2.py}
\caption{Using the \texttt{sun.constants} module.}
\label{code:constants_code}
\end{listing}

>>>>

\begin{listing}[H]
\pythoncode{pycode_util1.txt}
\caption{Using the \texttt{wcs} subpackage.}
\label{code:wcs_code}
\end{listing}

@@

The \texttt{sun.constants} module provides a number of solar-related 
constants in order to provide consistency in the calculations of derived solar 
values within SunPy, but also to the user. Every solar 
constant is provided as a \texttt{Constant} object as defined by the Astropy \texttt{units} package. Each 
\texttt{Constant} object defines a \texttt{Quantity}, a number associated with a unit, along with 
the constant's provenance (i.e., reference) and its uncertainty. Using 
Astropy's \texttt{Quantity} objects, any solar constant can easily be converted between 
different units, including between the SI or cgs unit systems, as can be seen in Listing~\ref{code:constants_code}.
As these objects inherit from 
NumPy's \texttt{ndarray}, they work well with standard representations of numbers.
For convenience, a number of shortcuts to frequently used constants are provided 
directly when importing the module. A larger list of constants can be 
accessed through an interface modeled on that provided by the SciPy constants 
package and is available as a dictionary called \texttt{physical\_constants}. 
To view them all quickly, a \texttt{print\_all()} function is available.

\begin{listing}[H]
\pythoncode{pycode_util2.txt}
\caption{Using the \texttt{sun.constants} module.}
\label{code:constants_code}
\end{listing}

### 2014-08-25 Sunpy_paper_0.4.tex
Comment out summary and tweaks to author list
Add an acknowledgements section
added a fix to display all quotes in codeblocks as straight quotes
small stuff and removed andy's fix for quotes

\usepackage{minted}
\definecolor{bg}{rgb}{0.95, 0.95, 0.95}
\usepackage{hyperref}

@@

@@

\input{solarsoft}

@@

%%% References
\bibliographystyle{stunat}
\bibliography{Sunpy_paper_0.4}{}

>>>>

\usepackage[section]{minted}
%\usepackage{upquote}
%\AtBeginDocument{%
%\def\PYZsq{\textquotesingle}%
%}
\definecolor{bg}{rgb}{0.95, 0.95, 0.95}

\newmintedfile[pythoncode]{pycon}{
bgcolor=bg,
fontfamily=tt,
linenos=true,
numberblanklines=true,
numbersep=12pt,
numbersep=5pt,
gobble=0,
frame=leftline,
framerule=0.4pt,
framesep=2mm,
funcnamehighlighting=true,
tabsize=4,
obeytabs=false,
mathescape=false
samepage=false, %with this setting you can force the list to appear on the same page
showspaces=false,
showtabs =false,
texcl=false,
}

\usepackage{hyperref}

@@

\usepackage{aas_macros}

@@

@@

\input{Summary}

\input{acknowledgements}

%%% References
\bibliographystyle{stunat}
\bibliography{Sunpy_paper_0.4,refs}{}
